\documentclass[12pt]{article}
\usepackage[left	=.75in,%
			top		=.65in,%			
			right	=.75in,%
			bottom	=.75in,%
			footskip = 3ex]{geometry}	% to adjust the margins
\usepackage[explicit]{titlesec}		% to change the section headers
\usepackage{enumitem}				% for modification of item lists
\usepackage{fancyhdr}
\pagestyle{fancy} 					% for the footer
%\usepackage[T1]{fontenc}			
\usepackage[default]{gillius}		% change to a sans-serif font
\usepackage[usenames, dvipsnames]{color}	% for gray text

%\renewcommand{\familydefault}{\sfdefault}

\setlength\parindent{0pt}
\setlist[itemize]{noitemsep, topsep=0pt}
\renewcommand{\labelitemi}{\raisebox{0.4ex}{\tiny$\bullet$}}

% reformat the section header
\titleformat{\section} %
  {\normalfont}{\thesection}{1em}{\MakeUppercase{\large #1}} %{\textbf{\MakeUppercase{\large #1}}}
\titlespacing\section{0pt}{12pt plus 3pt minus 2pt}{2pt plus 3pt minus 2pt}

\newcommand\textbox[1]{\parbox{.333\textwidth}{#1}}
\newcommand{\textlcr}[3]{\textbox{\textbf{#1}\hfill}\textbox{\hfil \textbf{#2}\hfil}\textbox{\hfill \textbf{#3}}}

\pagenumbering{gobble} % remove page numbering

\definecolor{mygray}{gray}{0.6}

\renewcommand{\headrulewidth}{0pt}	% remove horizontal line at top
\rfoot{\color{mygray} Latest version at \textit{https://github.com/nickchung114/LaTEX-Resume/blob/master/Nicholas\_Chung.pdf}}

\begin{document}
\begin{center}
	\textbf{\LARGE Nicholas Chung} \\ \vspace{.5ex}
	nickchung114@g.ucla.edu $\cdot$ (909) 979-7140 $\cdot$ www.linkedin.com/in/nc114 $\cdot$ US Citizen
\end{center}

\vspace{-8pt}
\smallskip
\section*{Education}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\textbf{Bachelor of Science in Electrical Engineering, UCLA}\hfill\textbf{Jun. 2017}
\begin{itemize}
\item GPA: 3.50
\end{itemize}

\textbf{Coursework to be completed as of}\hfill\textbf{Mar. 2017}
\begin{itemize}
\item EE: Digital Control of Physical Systems
\item CS: Fundamentals of Artificial Intelligence
\end{itemize}

\textbf{Coursework completed as of}\hfill\textbf{Dec. 2016}
\begin{itemize}
\item CS: Modeling and Simulation, Computer Science I/II, Discrete Structures, Intro to Algorithms
\item EE: Design Capstone, Digital Signal Processing, Intro to Digital Systems, Control Feedback Theory, Graph Theory, Analog Circuits,  Speech \& Image Processing
\end{itemize}

\section*{Projects}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\textlcr{Project Member}{Orchestra Anywhere}{Oct. 2016 - Mar. 2017}
\\ \textit{Final project for systems design capstone course using localization and gesture recognition to play music.}
\begin{itemize}
\item Built multi-threaded TCP/IP network using Python and C to interface Intel Edison's and MATLAB
\item Refactored 500 lines of Python and C code to improve readability and documentation (using Git)
\item Implemented, tested, and debugged gesture recognition based on user input through an IMU
\item Supported real-time gait-tracking development combining open-source software and windowing
\end{itemize}

\bigskip
\textlcr{Team Lead}{IEEE: Advanced Projects}{Oct. 2016 - Present}
\begin{itemize}
\item Integrating radio, IMU, and microcontroller modules to build a mini-quadcopter
\item Tested and debugged individual modules regarding SPI, I$^2$C, and low-side switching
\item Designed a 2-layer PCB using EAGLE to compactly contain surface-mount components
\end{itemize}

\bigskip
\textlcr{Project Member}{IEEE: NATCAR}{Sept. 2014 - Mar. 2015}
\begin{itemize}
\item Built components of the line-following car, including an H-bridge, AFE sensors, and a wave rectifier
\item Designed and printed a PCB using EAGLE to process input sensory data from a line sensor
\end{itemize}

\iffalse
\bigskip
\textlcr{Audio-Interface Clock}{Introduction to EE}{Jan. 2014 - Mar. 2014}
\begin{itemize}
\item Programmed using LabVIEW a finite-state machine for processing audio input
\item Implemented a circuit to detect audio cues, allowing interaction with the alarm clock
\end{itemize}
\fi

\section*{Experience}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\textlcr{Embedded Software Engineer}{Northrop Grumman}{Jul. 2017 - Present}
\begin{itemize}
\item Generated bi-directional traceability matrices using DOORS
\item Compiled and peer-reviewed software design document
\item Wrote MATLAB test scripts to automate Simulink test suites and custom report generation
\item Supported the design of software development infrastructure in ClearCase
\item Porting legacy code to newer GreenHills RTOS and debugging related errors
\end{itemize}

\bigskip
\textlcr{Team Member}{Project Premonition}{Nov. 2015 - Oct. 2016}
\\ \textit{Microsoft research aimed at detecting pathogens prior to outbreaks using drones and mosquito traps.}
\begin{itemize}
\item Translated existing MATLAB code to Simulink block diagram for easier controller simulation
\item Researched potential applications of a Kalman filter to supplement the PID code in Pixhawk
\end{itemize}

\bigskip
\textlcr{Student Intern}{EPSS Lab at UCLA}{Jun. 2016 - Oct. 2016}
\begin{itemize}
\item Developed schematics and pcb layouts for various component libraries following IPC standards
\item Debugged and collected measurements while testing various circuit boards
\end{itemize}

\section*{Leadership}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\textlcr{LA PDP Chapter Lead}{Northrop Grumman}{Oct. 2017 - Present}
\begin{itemize}
\item Coordinate Lunch \& Learn sessions to disseminate technical information to newer employees
\item Head two site councils and support their professional development activities
\end{itemize}

\bigskip
\textlcr{VP of Operations}{IEEE-HKN: Honors Society}{Sept. 2015 - Jun. 2016}
\begin{itemize}
\item Supported officers with weekly meetings and clarification of responsibilities
\item Coordinated Q/A panels, department townhalls, and professional-development workshops
\end{itemize}

\section*{Skills}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
\begin{itemize}
\item \textbf{CS}: Python, C++, Git, LaTEX, HTML/CSS
\item \textbf{EE}: MATLAB, Simulink, EAGLE Schematics, LabVIEW,  Altium, Logisim
\end{itemize}
\end{document}