\documentclass[12pt]{article}
\usepackage[left	=.75in,%
			top		=.65in,%			
			right	=.75in,%
			bottom	=.75in,%
			footskip = 3ex]{geometry}	% to adjust the margins
\usepackage[explicit]{titlesec}		% to change the section headers
\usepackage{enumitem}				% for modification of item lists
\usepackage{fancyhdr}
\pagestyle{fancy} 					% for the footer
%\usepackage[T1]{fontenc}			
\usepackage[default]{gillius}		% change to a sans-serif font
\usepackage[usenames, dvipsnames]{color}	% for gray text
\usepackage[letterspace=82]{microtype}

%\renewcommand{\familydefault}{\sfdefault}

\setlength\parindent{0pt}
\setlist[itemize]{itemsep=1pt, topsep=0pt, parsep=0pt}
\renewcommand{\labelitemi}{\raisebox{0.4ex}{\tiny$\bullet$}} % aligns the bullets with the center height of the line

% reformat the section header
\titleformat{\section} %
  {\normalfont}{\thesection}{1em}{\MakeUppercase{\large \lsstyle #1}} %{\textbf{\MakeUppercase{\large #1}}}
\titlespacing\section{0pt}{12pt plus 3pt minus 2pt}{2pt plus 3pt minus 2pt}

\newcommand\textbox[1]{\parbox{.333\textwidth}{#1}}
\newcommand{\textlcr}[3]{\textbox{\textbf{#1}\hfill}\textbox{\hfil \textbf{#2}\hfil}\textbox{\hfill \textbf{#3}}}

\newcommand\firstboxx[2]{\textbf{\fontsize{12.8}{15}\selectfont #1}, \textit{#2}}
\newcommand{\itemheader}[3]{\firstboxx{#1}{#2}\hfill#3}

\pagenumbering{gobble} % remove page numbering

\definecolor{mygray}{gray}{0.6}

\renewcommand{\headrulewidth}{0pt}	% remove horizontal line at top
\rfoot{\color{mygray} Latest version at \textit{https://github.com/nickchung114/LaTEX-Resume/blob/master/Nicholas\_Chung.pdf}}

\begin{document}
\begin{center}
	\textbf{\LARGE Nicholas Chung} \\ \vspace{.5ex}
	nychung@uci.edu $\cdot$ (909) 979-7140 $\cdot$ https://www.linkedin.com/in/nc114 $\cdot$ Irvine, CA
\end{center}

%\vspace{-8pt}
%\smallskip

\section*{Education}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
\itemheader{Masters in Computer Science}{UCI (GPA: 3.90)}{Oct. 2020 - Dec. 2021}
\begin{itemize}
\item Completed courses: Data Structures, Machine Learning and Data Mining, Neural Networks and Deep Learning, Fundamentals of Algorithms, Capstone Project
\end{itemize}

\smallskip
\itemheader{Bachelors in Electrical Engineering}{UCLA}{Sept. 2013 - Jun. 2017}

%\textbf{Relevant Coursework}
%\begin{itemize}
%\item CS: Modeling and Simulation, Computer Science I/II, Discrete Structures, Algorithms
%\item EE: Digital Signal Processing, Control Feedback Theory, Graph Theory, Speech \& Image Processing
%\end{itemize}

\section*{Projects}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\itemheader{Climbing Assistant}{[Tensorflow, Flutter, Dart]}{Aug. 2021 - Present}
\\ \textit{Mobile application using computer vision to estimate orientation and extrapolate center of mass}
\begin{itemize}
\item Developing in Flutter to incorporate Tensorflow pose estimation model with base application
\item Meeting regularly with two professors to review progress and action items for subsequent sprints
\end{itemize}

\bigskip
\itemheader{Obi Wan Coursenobi}{[React, Javascript, Python, MongoDB]}{Apr. 2021 - May. 2021}
\\ \textit{Capstone project and web application using MERN stack to visualize academic course dependencies}
\begin{itemize}
\item Designed webpage layout and used Agile methodology to complete development within 3 sprints
\item Implemented directed network graph using D3.js to illustrate class pre-requisite dependencies
\item Developed front-facing application to capture user interactions and present web features complementary to the network graph
\end{itemize}

\bigskip
\itemheader{Timbre Transfer}{[Tensorflow, Python]}{Jan. 2021 - Mar. 2021}
\\ \textit{Deep learning project utilizing CycleGAN to change the timbre of a melody}
\begin{itemize}
\item Pre-processed note samples from Magenta NSynth database to generate spectrogram dataset
\item Modified existing architecture to accept single-channel inputs and to mitigate checkboarding
\end{itemize}

\bigskip
\itemheader{Stock Prediction}{[C++, Tensorflow, Python]}{Jan. 2021 - Mar. 2021}
\\ \textit{Deep learning project using LSTM layers to predict stock prices and compile a portfolio}
\begin{itemize}
\item Reduced, regrouped, and formatted 20GB of stock transactions as input for machine learning
%\item Predicted overall stock changes for the following month
\item Constructed LSTM model and used it in conjunction with optimal stopping to decide on best price
\end{itemize}

%\itemheader{Orchestra Anywhere}{UCLA}{Oct. 2016 - Mar. 2017}
%\\ \textit{Undergraduate systems design capstone project using localization and gesture recognition to play music.}
%\begin{itemize}
%\item Built multi-threaded TCP/IP network using Python and C to interface Intel Edison's and MATLAB
%\item Refactored 500 lines of Python and C code to improve readability and documentation (using Git)
%\item Implemented, tested, and debugged gesture recognition based on user input through an IMU
%\item Supported real-time gait-tracking development combining open-source software and windowing
%\end{itemize}

\section*{Experience}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\itemheader{Proposal Analyst}{Northrop Grumman (T2)}{Aug. 2019 - Sept. 2020}
\begin{itemize}
%\item Developed a tool set (1000+ lines of Visual Basic) to automate requirement decomposition
\item Developed a Visual Basic tool set to automate the requirements decomposition process
\item Managed multiple multimillion-dollar competitive proposal and white paper efforts
%\item Coordinated with proposal teams to revise drafts and finalize desktop publishing activities
%\item Created output charts for and presented at strategic planning meetings
\end{itemize}

\bigskip
\itemheader{Sensors Engineer}{Northrop Grumman (T2)}{Jul. 2018 - Aug. 2019}
\begin{itemize}
\item Integrated cRIO and PC hardware with high-speed centrifuge to gather metrics on accelerometers
%\item Collaborated with lead software engineer to develop a LabView suite to tune and test gyroscopes
\item Developed SQL and MATLAB scripts to mine Oracle database and analyze gyroscope parameters
%\item Developed a script (500+ lines of SQL and MATLAB) to mine an Oracle database and analyze trends on combinations of sensor parameters
\item Collaborated with off-site and on-site teams to manage scheduling through GANTT charts
\end{itemize}

\bigskip
\itemheader{Associate Embedded Software Engineer}{Northrop Grumman (T1)}{Jul. 2017 - Jun. 2018}
\begin{itemize}
%\item Developed a script (1000+ lines of MATLAB) to automatically generate a Simulink system/ subsystem diagram and custom report from an interface controls document
\item Developed a MATLAB tool set to automatically generate a high-level systems interface diagram 
\item Generated bi-directional traceability matrices (DOORS) and compiled software design documents
%\item Compiled and peer-reviewed software design documents
\end{itemize}

%\section*{Leadership}
%\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

%\itemheader{FABLAB Committee Member}{Northrop Grumman}{Feb. 2018 - Jun. 2019}
%\begin{itemize}
%\item Drafted concept of operations to pitch fabrication lab to site executives and legal team
%\item Developed 3D printing fundamentals course and maintained 3D printers
%\end{itemize}

%\smallskip
%\itemheader{LA Pathways Chapter Lead}{Northrop Grumman}{Oct. 2017 - Dec. 2019}
%\begin{itemize}
%\item Coordinated technical lectures, discussion forums, cross-campus events, and all-hands meetings
%\item Worked with 80 entry-level rotational employees to address and resolve new hire concerns
%\end{itemize}

\section*{Skill Proficiencies}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
\begin{itemize}
\item \textbf{Language Competencies}: C++, React/Javascript, Python, SQL, Flutter/Dart
\item \textbf{Auxiliary Proficiencies}: MATLAB/Simulink, VBA, Git, LabView, HTML/CSS, DOORS
%\item \textbf{Software}: C++, Python, SQL, MATLAB/Simulink, VBA, Git, LabView, LaTEX, HTML/CSS, DOORS
%\item \textbf{Hardware}: CompactRIO, 3D printing, soldering
\end{itemize}
\end{document}