 \documentclass[12pt]{article}
\usepackage[left	=.75in,%
			top		=.65in,%			
			right	=.75in,%
			bottom	=.75in,%
			footskip = 3ex]{geometry}	% to adjust the margins
\usepackage[explicit]{titlesec}		% to change the section headers
\usepackage{enumitem}				% for modification of item lists
\usepackage{fancyhdr}
\pagestyle{fancy} 					% for the footer
%\usepackage[T1]{fontenc}			
\usepackage[default]{gillius}		% change to a sans-serif font
\usepackage[usenames, dvipsnames]{color}	% for gray text
\usepackage{soul}

%\renewcommand{\familydefault}{\sfdefault}

\setlength\parindent{0pt}
\setlist[itemize]{noitemsep, topsep=0pt}
\renewcommand{\labelitemi}{\raisebox{0.4ex}{\tiny$\bullet$}}
\sodef\letspa{}{.3em}{.5em plus1em}{1em plus.1em minus.1em}

% reformat the section header
\titleformat{\section} %
  {\normalfont}{\thesection}{1em}{\MakeUppercase{\large \letspa{#1}}} %{\textbf{\MakeUppercase{\large #1}}}
\titlespacing\section{0pt}{12pt plus 3pt minus 2pt}{2pt plus 3pt minus 2pt}

\newcommand\textbox[1]{\parbox{.333\textwidth}{#1}}
\newcommand{\textlcr}[3]{\textbox{\textbf{#1}\hfill}\textbox{\hfil \textbf{#2}\hfil}\textbox{\hfill \textbf{#3}}}

\pagenumbering{gobble} % remove page numbering

\definecolor{mygray}{gray}{0.6}

\renewcommand{\headrulewidth}{0pt}	% remove horizontal line at top
\rfoot{\color{mygray} Latest version at \textit{https://github.com/nickchung114/LaTEX-Resume/blob/master/Nicholas\_Chung.pdf}}

\begin{document}
\begin{center}
	\textbf{\LARGE Nicholas Chung} \\ \vspace{.5ex}
	nickchung114@g.ucla.edu $\cdot$ (909) 979-7140 $\cdot$ www.linkedin.com/in/nc114 $\cdot$ US Citizen
\end{center}

\vspace{-8pt}
\smallskip
\section*{Education}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\textbf{Bachelor of Science in Electrical Engineering, UCLA}\hfill\textbf{Jun. 2017}
\begin{itemize}
\item GPA: 3.50
\end{itemize}

\textbf{Relevant Coursework}
\begin{itemize}
\item CS: Modeling and Simulation, Computer Science I/II, Discrete Structures, Algorithms
\item EE: Digital Signal Processing, Control Feedback Theory, Graph Theory, Speech \& Image Processing
\end{itemize}

\section*{Experience}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\textlcr{Embedded Software Engineer}{Northrop Grumman}{Jul. 2017 - Present}
\begin{itemize}
\item Generated bi-directional traceability matrices using DOORS
\item Compiled and peer-reviewed software design document
\item Wrote MATLAB test scripts to automate Simulink test suites and custom report generation
\item Supported the design of software development infrastructure in ClearCase
\item Porting legacy code to newer GreenHills RTOS and debugging related errors
\end{itemize}

\bigskip
\textlcr{Team Member}{Project Premonition}{Nov. 2015 - Oct. 2016}
\\ \textit{Microsoft research aimed at detecting pathogens prior to outbreaks using drones and mosquito traps.}
\begin{itemize}
\item Translated existing MATLAB code to Simulink block diagram for easier controller simulation
\item Researched potential applications of a Kalman filter to supplement the PID code in Pixhawk
\end{itemize}

\section*{Projects}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\textlcr{Project Member}{Orchestra Anywhere}{Oct. 2016 - Mar. 2017}
\\ \textit{Final project for systems design capstone course using localization and gesture recognition to play music.}
\begin{itemize}
\item Built multi-threaded TCP/IP network using Python and C to interface Intel Edison's and MATLAB
\item Refactored 500 lines of Python and C code to improve readability and documentation (using Git)
\item Implemented, tested, and debugged gesture recognition based on user input through an IMU
\item Supported real-time gait-tracking development combining open-source software and windowing
\end{itemize}

\bigskip
\textlcr{Team Lead}{IEEE: Advanced Projects}{Oct. 2016 - Apr. 2017}
\begin{itemize}
\item Integrated radio, IMU, and microcontroller modules to build a mini-quadcopter
\item Tested and debugged individual modules regarding SPI, I$^2$C, and low-side switching
\item Designed a 2-layer PCB using EAGLE to compactly contain surface-mount components
\end{itemize}

\section*{Leadership}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\textlcr{LA PDP Chapter Lead}{Northrop Grumman}{Oct. 2017 - Present}
\begin{itemize}
\item Coordinate Lunch \& Learn sessions to disseminate technical information to newer employees
\item Head two site councils and support their professional development activities
\end{itemize}

\bigskip
\textlcr{VP of Operations}{IEEE-HKN: Honors Society}{Sept. 2015 - Jun. 2016}
\begin{itemize}
\item Supported officers with weekly meetings and clarification of responsibilities
\item Coordinated Q/A panels, department townhalls, and professional-development workshops
\end{itemize}

\section*{Skills}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
\begin{itemize}
\item \textbf{CS}: Python, C++, Git, LaTEX, HTML/CSS
\item \textbf{EE}: MATLAB, Simulink, EAGLE Schematics, LabVIEW,  Altium, Logisim
\end{itemize}
\end{document}