\documentclass[12pt]{article}
%\usepackage[thin]{roboto}
%\usepackage[T1]{fontenc}
%\usepackage{xltxtra}
%\setmainfont{LinBiolinum_R}
\usepackage[left	=.75in,%
			top		=.65in,%
			right	=.75in,%
			bottom	=.75in,%
			footskip = 3ex]{geometry}	% to adjust the margins
\usepackage[explicit]{titlesec}		% to change the section headers
\usepackage{enumitem}				% for modification of item lists
\usepackage{fancyhdr}
\pagestyle{fancy} 					% for the footer
%\usepackage[T1]{fontenc}			
%\usepackage[default]{gillius}		% change to a sans-serif font
\usepackage[usenames, dvipsnames]{color}	% for gray text

%\renewcommand{\familydefault}{\sfdefault}

\font\SectionHeaders="[LinBiolinum_R.otf]:letterspace=5" at 20pt

\setlength\parindent{0pt}
\setlist[itemize]{noitemsep, topsep=0pt}
\renewcommand{\labelitemi}{\raisebox{0.4ex}{\tiny$\bullet$}}

% reformat the section header
\titleformat{\section} %
  {\normalfont}{\thesection}{1em}{\textbf{\MakeUppercase{\large #1}}}
\titlespacing\section{0pt}{12pt plus 3pt minus 2pt}{2pt plus 3pt minus 2pt}

\newcommand\textbox[1]{\parbox{.333\textwidth}{#1}}
\newcommand{\textlcr}[3]{\textbox{\textbf{#1}\hfill}\textbox{\hfil \textbf{#2}\hfil}\textbox{\hfill \textbf{#3}}}

\pagenumbering{gobble}	% remove page numbering
\renewcommand{\headrulewidth}{0pt}	% remove horizontal line at top

\definecolor{mygray}{gray}{0.6}	% color for the footer
\rfoot{\color{mygray} Latest version at \textit{https://github.com/nickchung114/LaTEX-Resume/blob/master/Nicholas\_Chung.pdf}}

\begin{document}
\begin{center}
	\textbf{\LARGE Nicholas Chung} \\ \vspace{.5ex}
	nickchung114@g.ucla.edu $\cdot$ (909) 979-7140 $\cdot$ www.linkedin.com/in/nc114 $\cdot$ US Citizen
\end{center}

\vspace*{-15pt}
\section*{Education}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\textbf{Bachelor of Science in Electrical Engineering}\hfill\textbf{Jun. 2017}
\begin{itemize}
\item GPA: 
\end{itemize}

\textbf{Coursework to be completed as of}\hfill\textbf{Mar. 2017}
\begin{itemize}
\item EE: Systems Design Capstone, Digital Speech Processing II
\item CS: Modeling and Simulation of Biological Systems
\end{itemize}

\textbf{Coursework completed as of}\hfill\textbf{Dec. 2016}
\begin{itemize}
\item CS: Computer Science I/II, Discrete Structures, Introduction to Algorithms
\item EE: Digital Signal Processing, Intro to Digital Systems, Control Feedback Theory, Graph Theory, Analog Circuits,  Speech \& Image Processing
\end{itemize}

\section*{Projects}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\textlcr{Team Member}{Orchestra Anywhere}{Oct. 2016 - Present}
\\ \textit{Final project for capstone design course using localization and gesture recognition to play music.}
\begin{itemize}
\item Calibrating 9DoF sensors and filtering noise using a Kalman filter to classify measurements
\item Using TCP/IP sensor network to process IMU measurements and estimate user's location
\end{itemize}

\bigskip
\textlcr{Team Member}{IEEE: Advanced Projects}{Oct. 2016 - Present}
\begin{itemize}
\item Implemented SPI and I$^2$C on two microcontrollers to learn fundamental communication concepts
\item Building a mini-quadcopter that will have a PID controller and communicate with a computer 
\end{itemize}

\bigskip
\textlcr{Team Member}{IEEE: NATCAR}{Sept. 2014 - Mar. 2015}
\begin{itemize}
\item Built components of the line-following car, including an H-bridge, AFE sensors, and a wave rectifier
\item Designed and printed a PCB using EAGLE to process input sensory data from a line sensor
\end{itemize}

\iffalse
\bigskip
\textlcr{Audio-Interface Clock}{Introduction to EE}{Jan. 2014 - Mar. 2014}
\begin{itemize}
\item Programmed using LabVIEW a finite-state machine for processing audio input
\item Implemented a circuit to detect audio cues, allowing interaction with the alarm clock
\end{itemize}
\fi

\section*{Experience}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\textlcr{Team Member}{Project Premonition}{Nov. 2015 - Oct. 2016}
\\ \textit{Microsoft research aimed at detecting pathogens prior to outbreaks using drones and mosquito traps.}
\begin{itemize}
\item Translated existing MATLAB code to Simulink block diagram for easier controller simulation
\item Understand the PID control for position in the Pixhawk and where to add a Kalman filter
\end{itemize}

\bigskip
\textlcr{Student Intern}{EPSS Lab at UCLA}{Jun. 2016 - Oct. 2016}
\begin{itemize}
\item Developed schematics and pcb layouts for various component libraries following IPC standards
\item Debugged and collected measurements while testing various circuit boards
\end{itemize}

\section*{Leadership}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}

\textlcr{VP of Operations}{IEEE-HKN: Honors Society}{Sept. 2015 - Jun. 2016}
\begin{itemize}
\item Supported officers with weekly meetings and clarification of responsibilities
\item Coordinated Q/A panels, department townhalls, and professional-development workshops
\end{itemize}

\section*{Skills}
\vspace*{-1em}\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
\begin{itemize}
\item \textbf{CS}: Java, C, C++, HTML/CSS, Python, Git
\item \textbf{EE}: Altium, LTSpice, Logisim, MATLAB/Simulink, LabVIEW, LaTEX, Soldering
\end{itemize}
\end{document}